---
title: "2022 UK Dynasty League - Week 7"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
author: "Dan Coulton"
date: "`r Sys.Date()`"
css: custom.css
output:
  rmdformats::readthedown
---

```{r setup, include = F, message = F}
library(tidyverse)
library(jsonlite)
library(httr)
library(ffscrapr)
library(ffsimulator)
library(linprog)
library(kableExtra)
library(rmarkdown)
library(plotly)
library(formattable)
library(rmdformats)
library(shiny)
library(rvest)
library(xml2)
library(lubridate)
library(scales)

season <- 2022
no_of_qbs <- 2

league_id <- sleeper_userleagues('DanCoulton') %>% filter(league_name == 'UK Dynasty League ') %>% pull(league_id)
dynasty_conn <- sleeper_connect(season = season, league_id = league_id)

ff_league <- ff_league(dynasty_conn)

gameweek_start <- 1
gameweek_end <- 7
league_size <- as.numeric(ff_league$franchise_count)
sims <- 1000
draft_rounds <- 4
pp_uplift <- 1.175 #Historic 2021 of other dynasty was 17.5% higher for potential than actual

### In the pipeline ###
# Next week preview
# Add league history
# Add trade history

```

```{r get players, include = F, message = F}

if(!exists('get_players')) {get_players <- GET('https://api.sleeper.app/v1/players/nfl')}
json_players_parsed <- content(get_players,as='parsed')

datalist = list()
for (i in 1:length(json_players_parsed)) {
  df<-data.frame(t(unlist(json_players_parsed[[i]],recursive = TRUE,use.names = TRUE)))
  datalist[[i]] <- df
}
player_data <-bind_rows(datalist)

remove(df,datalist,i, json_players_parsed)

```

```{r KTC dynasty, echo = F}

KTC_dynasty_url <- read_html(paste0('https://keeptradecut.com/dynasty-rankings?page=0&filters=QB|WR|RB|TE|RDP&format=', no_of_qbs))

KTC = list()
KTC$Tier <- KTC_dynasty_url %>% html_nodes(xpath = '//*[@id="rankings-page-rankings"]/div/div/div/div[4]/p') %>% html_text
KTC$Player <- KTC_dynasty_url %>% html_nodes(xpath = '//*[@id="rankings-page-rankings"]/div/div/div/div[2]/p/a') %>% html_text
KTC$Value <- KTC_dynasty_url %>% html_nodes(xpath = '//*[@id="rankings-page-rankings"]/div/div/div/div[6]/p') %>% html_text
KTC$Info <- KTC_dynasty_url %>% html_nodes(xpath = '//*[@id="rankings-page-rankings"]/div/div/div/div[8]/div[4]/p[1]') %>% html_text %>% 
  gsub('\t', '', .) %>% gsub('\n', '', .) %>% gsub('\r', '', .)

df_KTC <- bind_cols(KTC) %>% 
  rowwise() %>% 
  mutate(Position = strsplit(Info, ' ')[[1]][1],
         Team = strsplit(Info, ' ')[[1]][3],
         Value = as.numeric(Value)) %>% 
  select(-Info) %>% 
  ungroup()

df_KTC_join <- df_KTC %>% 
  #filter(Position != 'RDP') %>% 
  mutate(Team = case_when(Team=='KCC' ~ 'KC',
                          Team=='JAC' ~ 'JAX',
                          Team=='SFO' ~ 'SF',
                          Team=='LVR' ~ 'LV',
                          Team=='NOS' ~ 'NO',
                          Team=='GBP' ~ 'GB',
                          Team=='TBB' ~ 'TB',
                          Team=='NEP' ~ 'NE',
                          Team=='FA' ~ NA_character_,
                          T ~ Team),
         Team = case_when(Player=='Will Fuller' ~ NA_character_,
                          Player=='Rob Gronkowski' ~ NA_character_,
                          Player=='Xavier Jones' ~ NA_character_,
                          Player=='Chris Herndon' ~ NA_character_,
                          Player=='Adam Humphries' ~ NA_character_,
                          Player=='T.Y. Hilton' ~ NA_character_,
                          Player=='Jordan Howard' ~ NA_character_,
                          Player=='Alex Collins' ~ NA_character_,
                          Player=='Wayne Gallman' ~ NA_character_,
                          Player=='Latavius Murray' ~ NA_character_,
                          Player=='Devonta Freeman' ~ NA_character_,
                          Player=='Kenyan Drake' ~ NA_character_,
                          Player=='Kelvin Harmon' ~ NA_character_,
                          Player=='CJ Verdell' ~ NA_character_,
                          Player=='Emmanuel Sanders' ~ NA_character_,
                          Player=='Kyle Phillips' ~ 'TEN',
                          T ~ Team),
         Player = str_remove(Player, c(' Jr.')),
         Player = str_remove(Player, c(' III')),
         Player = str_remove(Player, c(' II')),
         Player = str_remove(Player, c(' IV')),
         Player = case_when(Player=='D.J. Moore' ~ 'DJ Moore',
                            Player=='Gabriel Davis' ~ 'Gabe Davis',
                            Player=='Mitchell Trubisky' ~ 'Mitch Trubisky',
                            Player=='Josh Palmer' ~ 'Joshua Palmer',
                            Player=='D.J. Chark' ~ 'DJ Chark',
                            Player=='Will Fuller' ~ 'William Fuller',
                            Player=='Robby Anderson' ~ 'Robbie Anderson',
                            Player=='Jeffery Wilson' ~ 'Jeff Wilson',
                            Player=="D'Wayne Eskridge" ~ 'Dee Eskridge',
                            Player=='Olabisi Johnson' ~ 'Bisi Johnson',
                            Player=='Kyle Phillips' ~ 'Kyle Philips',
                            Player=='Lamical Perine' ~ "La'Mical Perine",
                            T ~ Player)) %>% 
  left_join(player_data[,c('full_name','team','position','player_id')], by=c('Player'='full_name', 'Position'='position', 'Team'='team'))

# df_KTC_join %>% 
#   filter(is.na(player_id)) %>% 
#   print(n=100)

```

```{r KTC fantasy, echo = F}

KTC_fantasy_url <- read_html(paste0('https://keeptradecut.com/fantasy-rankings?page=0&filters=QB|WR|RB|TE&format=', no_of_qbs))

KTC_fantasy = list()
KTC_fantasy$Tier <- KTC_fantasy_url %>% html_nodes(xpath = '//*[@id="rankings-page-rankings"]/div/div/div/div[4]/p') %>% html_text
KTC_fantasy$Player <- KTC_fantasy_url %>% html_nodes(xpath = '//*[@id="rankings-page-rankings"]/div/div/div/div[2]/p/a') %>% html_text
KTC_fantasy$Value <- KTC_fantasy_url %>% html_nodes(xpath = '//*[@id="rankings-page-rankings"]/div/div/div/div[6]/p') %>% html_text
KTC_fantasy$Info <- KTC_fantasy_url %>% html_nodes(xpath = '//*[@id="rankings-page-rankings"]/div/div/div/div[8]/div[4]/p[1]') %>% html_text %>% 
  gsub('\t', '', .) %>% gsub('\n', '', .) %>% gsub('\r', '', .)

df_KTC_fantasy <- bind_cols(KTC_fantasy) %>% 
  rowwise() %>% 
  mutate(Position = strsplit(Info, ' ')[[1]][1],
         Team = strsplit(Info, ' ')[[1]][3],
         Value = as.numeric(Value)) %>% 
  select(-Info) %>% 
  ungroup()

df_KTC_fantasy_join <- df_KTC_fantasy %>% 
  filter(Position != 'RDP') %>% 
  mutate(Team = case_when(Team=='KCC' ~ 'KC',
                          Team=='JAC' ~ 'JAX',
                          Team=='SFO' ~ 'SF',
                          Team=='LVR' ~ 'LV',
                          Team=='NOS' ~ 'NO',
                          Team=='GBP' ~ 'GB',
                          Team=='TBB' ~ 'TB',
                          Team=='NEP' ~ 'NE',
                          Team=='FA' ~ NA_character_,
                          T ~ Team),
         Team = case_when(Player=='Will Fuller' ~ NA_character_,
                          Player=='Rob Gronkowski' ~ NA_character_,
                          Player=='Xavier Jones' ~ NA_character_,
                          Player=='Chris Herndon' ~ NA_character_,
                          Player=='Adam Humphries' ~ NA_character_,
                          Player=='T.Y. Hilton' ~ NA_character_,
                          Player=='Jordan Howard' ~ NA_character_,
                          Player=='Alex Collins' ~ NA_character_,
                          Player=='Wayne Gallman' ~ NA_character_,
                          Player=='Latavius Murray' ~ NA_character_,
                          Player=='Devonta Freeman' ~ NA_character_,
                          Player=='Kenyan Drake' ~ NA_character_,
                          Player=='Kelvin Harmon' ~ NA_character_,
                          Player=='CJ Verdell' ~ NA_character_,
                          Player=='Emmanuel Sanders' ~ NA_character_,
                          Player=='Kyle Phillips' ~ 'TEN',
                          T ~ Team),
         Player = str_remove(Player, c(' Jr.')),
         Player = str_remove(Player, c(' III')),
         Player = str_remove(Player, c(' II')),
         Player = str_remove(Player, c(' IV')),
         Player = case_when(Player=='D.J. Moore' ~ 'DJ Moore',
                            Player=='Gabriel Davis' ~ 'Gabe Davis',
                            Player=='Mitchell Trubisky' ~ 'Mitch Trubisky',
                            Player=='Josh Palmer' ~ 'Joshua Palmer',
                            Player=='D.J. Chark' ~ 'DJ Chark',
                            Player=='Will Fuller' ~ 'William Fuller',
                            Player=='Robby Anderson' ~ 'Robbie Anderson',
                            Player=='Jeffery Wilson' ~ 'Jeff Wilson',
                            Player=="D'Wayne Eskridge" ~ 'Dee Eskridge',
                            Player=='Olabisi Johnson' ~ 'Bisi Johnson',
                            Player=='Kyle Phillips' ~ 'Kyle Philips',
                            Player=='Lamical Perine' ~ "La'Mical Perine",
                            T ~ Player)) %>% 
  left_join(player_data[,c('full_name','team','position','player_id')], by=c('Player'='full_name', 'Position'='position', 'Team'='team'))

# df_KTC_fantasy_join %>%
#   filter(is.na(player_id)) %>%
#   print(n=100)

```

```{r user info, include = F, message = F}

rostersRaw <- GET(paste("https://api.sleeper.app/v1/league/",league_id,"/rosters",sep=""))
rostersParsed <- content(rostersRaw,as="parsed")
usersRaw <- fromJSON(paste("https://api.sleeper.app/v1/league/",league_id,"/users",sep=""), flatten = TRUE)

datalist = list()
for (i in 1:league_size) {
  df<-data.frame(t(unlist(rostersParsed[i]))) %>%
    select(roster_id, owner_id, starts_with('players')) %>%
    mutate(pick1 = paste0(season+1, ' Mid 1st'), pick2 = paste0(season+1, ' Mid 2nd'), pick3 = paste0(season+1, ' Mid 3rd'),
           pick4 = paste0(season+1, ' Mid 4th'), pick5 = paste0(season+2, ' Mid 1st'), pick6 = paste0(season+2, ' Mid 2nd'),
           pick7 = paste0(season+2, ' Mid 3rd'), pick8 = paste0(season+2, ' Mid 4th')) %>% 
    pivot_longer(cols = starts_with(c('player', 'pick')), names_to = 'player_no', values_to = 'player_id') %>%
    left_join(player_data[, c('full_name', 'position', 'player_id', 'team')], by = 'player_id')
  
  datalist[[i]] <- df
}
rosters <- data.frame(bind_rows(datalist)) %>% 
  mutate(full_name = if_else(is.na(full_name), player_id, full_name)) %>% 
  left_join(usersRaw[, c('user_id', 'display_name', 'metadata.team_name')], by = c('owner_id' = 'user_id')) %>% 
  rename(Manager = display_name)
rm(datalist)



########### User Info ###########
datalist = list()
for (i in 1:league_size) {
  df<-data.frame(t(unlist(rostersParsed[i]))) %>%
    select(owner_id, roster_id)
  
  datalist[[i]] <- df
}
user_info <- data.frame(bind_rows(datalist)) %>% 
  left_join(usersRaw[, c('user_id', 'display_name', 'metadata.team_name')], by = c('owner_id' = 'user_id')) %>% 
  rename(Manager = display_name)

```

```{r get matchups, include = F, message = F}

datalist_gameweek = list()
for (i in gameweek_start:14) {
  matchupRaw <- GET(paste('https://api.sleeper.app/v1/league/',league_id,'/matchups/', i, sep=""))
  matchupParsed <- content(matchupRaw, as="parsed")
  
  datalist_matchup = list()
  for (j in 1:league_size) {
    df <- data.frame(t(unlist(matchupParsed[j]))) %>% 
      select(roster_id, matchup_id, starts_with('players_points')) %>% 
      pivot_longer(cols = starts_with('players_points'), names_to = 'player_id', values_to = 'points') %>% 
      mutate(player_id = substr(player_id, 16, length(player_id)),
             matchup_id = as.numeric(matchup_id),
             points = as.numeric(points))
    
    starters <- data.frame(t(unlist(matchupParsed[j]))) %>% 
      select(roster_id, matchup_id, starts_with('starters'), -starts_with('starters_')) %>% 
      pivot_longer(cols = starts_with('starters'), names_to = 'starter_id', values_to = 'player_id') %>% 
      mutate(starter_ind = 1)
    
    df <- df %>% 
      left_join(starters[c('player_id', 'starter_ind')], by = 'player_id')
      
    datalist_matchup[[j]] <- df
  }
  datalist_gameweek[[i]] <-bind_rows(datalist_matchup) %>% 
    mutate(gameweek = i)
}
matchup_data <-bind_rows(datalist_gameweek) %>% 
  left_join(player_data[, c('full_name', 'position', 'player_id', 'team')], by = 'player_id') %>% 
  mutate(full_name = if_else(position=='DEF', player_id, full_name),
         starter_ind = if_else(is.na(starter_ind), 0, 1)) %>% 
  left_join(user_info[, c('roster_id', 'Manager')], by = 'roster_id') %>% 
  rename(Points = points)

remove(df,datalist_matchup, datalist_gameweek, i, j, matchupRaw, matchupParsed)

matchup_id <- matchup_data %>% 
  distinct(roster_id, matchup_id, gameweek) %>% 
  left_join(x=., y=., by = c('matchup_id', 'gameweek')) %>% 
  rename(roster_id = roster_id.x, opponent_id = roster_id.y) %>% 
  filter(roster_id!=opponent_id)

```

```{r get historic scores, include = F, message = F}

# league_id2021 <- '659068468825530368'

### 2021 ###
# datalist_gameweek = list()
# for (i in gameweek_start:17) {
#   matchupRaw <- GET(paste('https://api.sleeper.app/v1/league/',league_id2021,'/matchups/', i, sep=""))
#   matchupParsed <- content(matchupRaw, as="parsed")
# 
#   datalist_matchup = list()
#   for (j in 1:league_size) {
#     df <- data.frame(t(unlist(matchupParsed[j]))) %>%
#       select(roster_id, points)
# 
#     datalist_matchup[[j]] <- df
#   }
#   datalist_gameweek[[i]] <-bind_rows(datalist_matchup) %>%
#     mutate(gameweek = i)
# }
# matchup_data2021 <-bind_rows(datalist_gameweek) %>%
#   mutate(season = 2021)

### 2022 ###
# datalist_gameweek = list()
# for (i in gameweek_start:gameweek_end) {
#   matchupRaw <- GET(paste('https://api.sleeper.app/v1/league/',league_id,'/matchups/', i, sep=""))
#   matchupParsed <- content(matchupRaw, as="parsed")
#   
#   datalist_matchup = list()
#   for (j in 1:league_size) {
#     df <- data.frame(t(unlist(matchupParsed[j]))) %>% 
#       select(roster_id, points)
#     
#     datalist_matchup[[j]] <- df
#   }
#   datalist_gameweek[[i]] <-bind_rows(datalist_matchup) %>% 
#     mutate(gameweek = i)
# }
# matchup_data2022 <-bind_rows(datalist_gameweek) %>% 
#   mutate(season = season) %>% 
#   filter(gameweek<=gameweek_end)
# 
# # score_data_historic <- bind_rows(matchup_data2019, matchup_data2020, matchup_data2021, matchup_data2022)
# # rm(matchup_data2019, matchup_data2020, matchup_data2021, matchup_data2022, datalist_gameweek, datalist_matchup)
# score_data_historic <- bind_rows(matchup_data2022)
# rm(matchup_data2022, datalist_gameweek, datalist_matchup)

```

```{r calculate potential points, include = F}

datalist_i = list()
datalist_j = list()
for (i in gameweek_start:gameweek_end) {
  for (j in 1:league_size) {
    match_result <- matchup_data %>% 
      filter(roster_id==j, gameweek==i)
    
    constraints_matrix=matrix(c(match_result$position=='QB',
                                match_result$position=='RB',
                                match_result$position=='WR',
                                match_result$position=='TE',
                                match_result$position=='QB',
                                match_result$position=='RB',
                                match_result$position=='WR',
                                match_result$position=='TE'),
                              byrow=T,nrow=8)
    
    objective_vector <- c(match_result$Points)
    constraints_matrix <- rbind(constraints_matrix, diag(dim(match_result)[1]), rep(1,dim(match_result)[1]))
    constraints_vector <- c(1, 2, 3, 1, 2, 5, 6, 4, rep(1,dim(match_result)[1]), 10)
    
    sol_pp <- lp(direction='max',objective.in = objective_vector, const.rhs = constraints_vector,
                 const.mat = constraints_matrix, const.dir = c(rep('>=',4), rep('<=',4), rep('<=',dim(match_result)[1]), '='), all.bin = T)
    sol_pp$solution
    sol_pp$objval
    
    datalist_j[[j]] <- match_result %>% mutate(pp_starter = sol_pp$solution, potential_points = pp_starter * Points)
  }
  datalist_i[[i]] <-bind_rows(datalist_j)
}
pp_player <- bind_rows(datalist_i)
rm(datalist_i, datalist_j, sol_pp, match_result, constraints_matrix, objective_vector, constraints_vector, i, j)

pp_week <- pp_player %>% 
  group_by(gameweek, roster_id, Manager) %>% 
  summarise(pp = sum(potential_points)) %>% 
  left_join(matchup_id[, c('opponent_id', 'roster_id', 'gameweek')], by = c('gameweek', 'roster_id')) %>% 
  left_join(x=., y=.[, c('gameweek', 'opponent_id', 'pp')], by = c('gameweek', 'roster_id' = 'opponent_id')) %>% 
  rename(pp = pp.x, pp_opponent = pp.y) %>% 
  mutate(win = if_else(pp > pp_opponent, 1,
                       if_else(pp_opponent > pp, 0, 0.5)))

pp_season <- pp_week %>% 
  group_by(Manager) %>% 
  summarise(Wins = sum(win),
            Points = sum(pp)) %>% 
  arrange(desc(Wins), desc(Points)) %>% 
  mutate(Rank = seq.int(nrow(.))) %>% 
  select(Rank, Manager, Wins, Points)

pp_weekly_matchup <- pp_week %>% 
  filter(gameweek==gameweek_end) %>% 
  left_join(matchup_id[, c('matchup_id', 'roster_id', 'gameweek')], by = c('roster_id', 'gameweek')) %>% 
  left_join(x=., y=.[, c('Manager', 'opponent_id')], by = c('roster_id' = 'opponent_id')) %>% 
  mutate(roster_id  = as.numeric(roster_id)) %>% 
  arrange(matchup_id, roster_id) %>% 
  ungroup() %>% 
  filter(matchup_id==lead(matchup_id)) %>% 
  rename(pp.x = pp, pp.y = pp_opponent) %>% 
  select(-win, -roster_id, -opponent_id)

```

------------------------------------------------------------------------

# Playoff Hunt

## Current Standings

The hunt for the playoffs as it stands. All-play is the record if all teams were to play each other every week. xWins is the number of wins you would have expected so far based on the all-play record. The playoff and bye % is calculated by calculating player scores since 2012 based on their rank and sampling these to give a score for each simulation. The optimal lineup is calculated and then an efficiency score is calculated to give the starting lineup score. **`r as.character(sims)`** different seasons have been simulated using the wins to date and the remaining fixtures for each team. Strength of roster is taken into account in these calculations.

```{r playoff hunt, echo = F, message = F}

pts_week <- matchup_data %>% 
  filter(starter_ind==1) %>% 
  group_by(gameweek, roster_id, Manager) %>% 
  summarise(pts = sum(Points)) %>% 
  left_join(matchup_id[, c('opponent_id', 'roster_id', 'gameweek')], by = c('gameweek', 'roster_id')) %>% 
  left_join(x=., y=.[, c('gameweek', 'opponent_id', 'pts')], by = c('gameweek', 'roster_id' = 'opponent_id')) %>% 
  rename(pts = pts.x, pts_opponent = pts.y) %>% 
  mutate(win = if_else(pts > pts_opponent, 1,
                       if_else(pts_opponent > pts, 0, 0.5))) %>% 
  ungroup %>% 
  group_by(gameweek) %>% 
  mutate(all_play = rank(pts)-1) %>% 
  left_join(matchup_id[, c('matchup_id', 'roster_id', 'gameweek')], by = c('roster_id', 'gameweek'))

scoring_history <- ffscrapr::ff_scoringhistory(dynasty_conn, season = 2012:2021)
bye_weeks <- ffs_latest_rankings(type = 'draft') %>% 
  select(team, bye) %>% distinct() %>% filter(team != 'FA') %>%
  mutate(team = case_when(team=='KCC' ~ 'KC',
                          team=='TBB' ~ 'TB',
                          team=='SFO' ~ 'SF',
                          team=='GBP' ~ 'GB',
                          team=='LVR' ~ 'LV',
                          team=='NOS' ~ 'NO',
                          team=='NEP' ~ 'NE',
                          T ~ team))
latest_rankings <- ffs_latest_rankings(type = "draft")
latest_rankings_weekly <- ffs_latest_rankings(type = "week") %>%
  left_join(bye_weeks, by = 'team')
rosters_ffs <- ffs_rosters(dynasty_conn)
lineup_constraints <- ffs_starter_positions(dynasty_conn)
league_info <- ffscrapr::ff_league(dynasty_conn)
actual_schedule <- matchup_id %>% 
  select(week=gameweek, franchise_id=roster_id, opponent_id) %>% 
  mutate(league_id = league_id)

adp_outcomes <- ffs_adp_outcomes(
  scoring_history = scoring_history,
  gp_model = "simple", # or "none"
  pos_filter = c("QB","RB","WR","TE", 'K', 'DST')
)

projected_scores <- ffs_generate_projections(
  adp_outcomes = adp_outcomes,
  latest_rankings = latest_rankings,
  n_seasons = sims, # number of seasons
  weeks = 1:14, # specifies which weeks to generate projections for
  rosters = rosters_ffs # optional, reduces the sample to just rostered players
)

projected_scores_weekly <- ffs_generate_projections(
  adp_outcomes = adp_outcomes,
  latest_rankings = latest_rankings_weekly,
  n_seasons = sims, # number of seasons
  weeks = 1:14, # specifies which weeks to generate projections for
  rosters = rosters_ffs # optional, reduces the sample to just rostered players
)

roster_scores <- ffs_score_rosters(
  projected_scores = projected_scores,
  rosters = rosters_ffs
)

roster_scores_weekly <- ffs_score_rosters(
  projected_scores = projected_scores_weekly,
  rosters = rosters_ffs
)

optimal_scores <- ffs_optimise_lineups(
  roster_scores = roster_scores,
  lineup_constraints = lineup_constraints,
  lineup_efficiency_mean = 0.775,
  lineup_efficiency_sd = 0.05,
  best_ball = FALSE, # or TRUE
  pos_filter = c("QB","RB","WR","TE","K")
)

optimal_scores_weekly <- ffs_optimise_lineups(
  roster_scores = roster_scores_weekly,
  lineup_constraints = lineup_constraints,
  lineup_efficiency_mean = 0.775,
  lineup_efficiency_sd = 0.05,
  best_ball = FALSE, # or TRUE
  pos_filter = c("QB","RB","WR","TE","K")
)

schedules <- ffs_repeat_schedules(actual_schedule, n=sims)

summary_week <- ffs_summarise_week(optimal_scores, schedules) %>% 
  left_join(.[, c('season', 'week', 'franchise_name', 'optimal_score')], by = c('season', 'week', 'opponent_name'='franchise_name'), suffix = c('', '_opponent')) %>% 
  left_join(pts_week[, c('pts', 'pts_opponent', 'gameweek', 'roster_id', 'win', 'all_play', 'Manager')], by = c('week'='gameweek', 'franchise_id'='roster_id')) %>% 
  left_join(pp_week[, c('gameweek', 'roster_id', 'pp', 'pp_opponent', 'win')], by = c('week'='gameweek', 'franchise_id'='roster_id'), suffix = c('', '_pp')) %>% 
  mutate(selected_pts = if_else(week>gameweek_end, team_score, pts),
         selected_win = if_else(week>gameweek_end, if_else(result=='W', 1, 0), win),
         selected_all_play = if_else(week>gameweek_end, allplay_wins, all_play),
         selected_pp = if_else(week>gameweek_end, optimal_score, pp),
         selected_pp_opponent = if_else(week>gameweek_end, optimal_score_opponent, pp_opponent),
         selected_pp_win = if_else(week>gameweek_end, if_else(optimal_score>optimal_score_opponent, 1, 0), win_pp),
         nxt_wk_win = if_else(week==gameweek_end+1, selected_win, 0))

summary_week_weekly <- ffs_summarise_week(optimal_scores_weekly, schedules) %>% 
  left_join(.[, c('season', 'week', 'franchise_name', 'optimal_score')], by = c('season', 'week', 'opponent_name'='franchise_name'), suffix = c('', '_opponent')) %>% 
  left_join(pts_week[, c('pts', 'pts_opponent', 'gameweek', 'roster_id', 'win', 'all_play', 'Manager')], by = c('week'='gameweek', 'franchise_id'='roster_id')) %>% 
  left_join(pp_week[, c('gameweek', 'roster_id', 'pp', 'pp_opponent', 'win')], by = c('week'='gameweek', 'franchise_id'='roster_id'), suffix = c('', '_pp')) %>% 
  mutate(selected_pts = if_else(week>gameweek_end, team_score, pts),
         selected_win = if_else(week>gameweek_end, if_else(result=='W', 1, 0), win),
         selected_all_play = if_else(week>gameweek_end, allplay_wins, all_play),
         selected_pp = if_else(week>gameweek_end, optimal_score, pp),
         selected_pp_opponent = if_else(week>gameweek_end, optimal_score_opponent, pp_opponent),
         selected_pp_win = if_else(week>gameweek_end, if_else(optimal_score>optimal_score_opponent, 1, 0), win_pp),
         nxt_wk_win = if_else(week==gameweek_end+1, selected_win, 0))

table_sim <- summary_week %>%
  group_by(season, Manager) %>%
  summarise(Wins = sum(selected_win),
            Points = sum(selected_pts),
            PPoints = sum(selected_pp),
            Upcoming = sum(nxt_wk_win)) %>%
  arrange(desc(Wins), desc(Points), .by_group = T) %>%
  mutate(Position = row_number(),
         Playoff = if_else(Position<=6, 1, 0),
         Bye = if_else(Position<=2, 1, 0)) %>%
  arrange(Playoff, PPoints, .by_group = T) %>%
  mutate(Draft_Pos = row_number()) %>%
  ungroup

sim_wins <- table_sim %>%
  group_by(Manager) %>%
  summarise(`Playoff %` = round(mean(Playoff)*100, 1),
            `Bye %` = round(mean(Bye)*100, 1))

sim_draft <- table_sim %>%
  group_by(Manager, Draft_Pos) %>%
  summarise(Count = round(n()/sims, 3)) %>%
  pivot_wider(id_cols = 'Manager', names_from = 'Draft_Pos', values_from = 'Count') %>%
  left_join(sim_wins[, c('Manager', 'Playoff %')], by = 'Manager') %>%
  replace(is.na(.), 0) %>% 
  mutate(Playoffs = `Playoff %`/100,
         Order = (`1`*1 + `2`*2 + `3`*3 + `4`*4 + `5`*5 + `6`*6 +Playoffs*9.5)) %>% # 9.5 average of 7-12
  arrange(Order) %>%
  select(Manager, `1`, `2`, `3`, `4`, `5`, `6`, Playoffs)

# summary_season <- ffs_summarise_season(summary_week) %>% 
#   left_join(user_info[, c('roster_id', 'Manager')], by = c('franchise_id'='roster_id'))

summary_season <- summary_week %>% 
  group_by(season, Manager, franchise_id) %>% 
  summarise(h2h_wins = sum(selected_win),
            points_for = sum(selected_pts))
# summary_simulation <- ffs_summarise_simulation(summary_season)

```

``` {r current table, echo = F, message = F}

pts_season <- pts_week %>%
  filter(gameweek<=gameweek_end) %>% 
  group_by(Manager) %>% 
  summarise(Wins = sum(win),
            Points = sum(pts),
            All_Play = sum(all_play)) %>% 
  arrange(desc(Wins), desc(Points)) %>% 
  mutate(`All-Play` = paste0(All_Play,'-', (league_size-1)*(gameweek_end-gameweek_start+1)-All_Play),
         xWins = round(All_Play/(league_size-1), 1),
         WOE = Wins - xWins,
         Position = league_size + 1 - rank(Wins + Points/10000)) %>% 
  left_join(sim_wins, by = 'Manager')

pts_season %>% 
  select(Position, Manager, Wins, Points, `All-Play`, xWins, `Playoff %`, `Bye %`) %>%
  knitr::kable(format = 'html', align = c('c', 'l', rep('c', 6)), escape = F) %>% 
  kable_styling(bootstrap_options = c('striped', 'responsive', 'hover'),
                full_width = F,
                position = 'left') %>% 
  row_spec(1:2, bold = T, color = 'white', background = '#0080ff') %>% 
  row_spec(3:6, bold = T, color = 'white', background = '#79c973') %>% 
  row_spec(7:12, bold = T, color = 'white', background = '#ff6666')

```

## Wins over Expectation

Wins over expectation (WOE) looks at the relationship between actual wins and all-play wins. This shows how lucky or unlucky a team has been with the schedule.

The dots on the chart below show how many wins the team have, whilst the arrow shows where they should actually be if the H2H format wasn't in place. Teams with arrows pointing right can count themselves unlucky, whilst teams with arrows pointing left are fortunate to have as many wins as they do.

``` {r wins vs expectation, echo = F, message = F, dev.args = list(bg = 'transparent')}

pts_season %>% 
  mutate(Manager = factor(Manager, levels = Manager)) %>% 
  ggplot(aes(y = fct_reorder(Manager, Wins*100+xWins), color = Manager)) +
  geom_point(aes(x=Wins), alpha = 0.8, size = 2) +
  geom_segment(aes(x = Wins,
                   xend = xWins,
                   y = Manager,
                   yend = Manager),
               size = 1,
               alpha = 0.75,
               lineend = "round",
               linejoin = "mitre",
               arrow = ggplot2::arrow(angle = 30,length = ggplot2::unit(6, "points"),type = "closed")) +
  geom_text(aes(x = (xWins + Wins)/2, label = round(Wins-xWins, 1)),
            hjust = 0.5, vjust = -0.5) +
  # geom_text(aes(x = Wins_pct, y = Manager, label = "Wins", vjust = -0.75)) +
  # geom_text(aes(x = xWins_pct, y = Manager, label = "xWins", vjust = -0.75)) +
  scale_x_continuous(labels = scales::number_format(),limits = c(0, gameweek_end)) +
  scale_color_discrete(guide = "none") +
  xlab("Wins") +
  ylab(NULL) +
  theme_minimal() +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        plot.title.position = "plot") +
  labs(title = glue::glue("Schedule Luck"),
       subtitle = glue::glue("Difference between H2H Wins and xWins based on All-Play - The arrow shows where you deserve to be"))

```

**`r pts_season %>% filter(WOE == max(WOE)) %>% pull(Manager)`** has been the luckiest so far, with **`r pts_season %>% filter(WOE == max(WOE)) %>% pull(WOE) %>% nth(1)`** more wins than expected.

**`r pts_season %>% filter(WOE == min(WOE)) %>% pull(Manager)`** can feel hard done by, with **`r pts_season %>% filter(WOE == min(WOE)) %>% mutate(WOE = -WOE) %>% pull(WOE) %>% nth(1)`** fewer wins than expected.

<br>

## Win Projections

The following chart shows the distribution of total expected wins over the season. Any wins so far have been included in the calculation, and you would expect the spread to reduce as the season progresses and the win totals become more certain.

``` {r total win projections, echo = F, message = F, warning = F, dev.args = list(bg = 'transparent')}

summary_season %>% 
  left_join(summary_season %>% group_by(Manager) %>% summarise(Wins=sum(h2h_wins)), by = 'Manager') %>%
  ggplot(aes(x = h2h_wins, y = fct_reorder(Manager, Wins), fill = Manager)) +
  ggridges::geom_density_ridges(
    stat = "binline",
    color = "white",
    binwidth = 1,
    scale = 1.3,
    alpha = 0.8,
    show.legend = FALSE
  ) +
  scale_x_continuous(breaks = seq.int(0, max(summary_season$h2h_wins) + 1, by = 2)) +
  xlab("Season Wins") +
  ylab(NULL) +
  theme_minimal() +
  theme(
    # legend.position = "none",
    panel.grid.major.y = ggplot2::element_blank(),
    panel.grid.minor.x = ggplot2::element_blank(),
    plot.title.position = "plot"
  ) +
  ggplot2::labs(title = glue::glue("Distribution of Season Win Totals - {sims} Simulated Seasons"),
                subtitle = glue::glue("{league_info$league_name}"))

```

## Projected Season Rank

Using the win totals from the chart above, the following chart shows the likelihood of each team finishing in a given position.

``` {r projected season rank, echo = F, message = F, warning = F, dev.args = list(bg = 'transparent')}

summary_season %>% 
  left_join(summary_season %>% group_by(Manager) %>% summarise(Wins=sum(h2h_wins)), by = 'Manager') %>%
  group_by(season) %>% 
  arrange(desc(h2h_wins), desc(points_for), .by_group = T) %>% 
  mutate(Position = row_number()) %>% 
  ggplot(aes(x = fct_reorder(Manager, -Wins), color = Manager, fill = Manager)) +
  ggplot2::geom_bar() +
  ggplot2::scale_x_discrete(guide = ggplot2::guide_axis(position = "none"))+
  ggplot2::facet_wrap(~ Position) +
  ggplot2::xlab(NULL) +
  ggplot2::ylab("Number of Seasons") +
  ggplot2::theme_minimal() +
  ggplot2::theme(
    panel.grid.major.x = ggplot2::element_blank(),
    plot.title.position = "plot",
    plot.caption.position = "plot"
  ) +
  ggplot2::labs(
    title = glue::glue("Final Season Rank - {sims} Simulated Seasons"),
    subtitle = glue::glue("{league_info$league_name}"),
    fill = "Manager",
    color = "Manager"
  )

```

## Point Projections for Week `r gameweek_end+1`

The following chart shows the distribution of points for the upcoming week.

``` {r upcoming week point projections, echo = F, message = F, warning = F, dev.args = list(bg = 'transparent')}

summary_week_weekly %>% 
  filter(week==gameweek_end+1) %>% 
  left_join(summary_week %>% group_by(Manager) %>% summarise(Score=sum(team_score)), by = 'Manager') %>% 
  ggplot(aes(x = team_score, y = fct_reorder(Manager, Score), fill = Manager)) +
  ggridges::geom_density_ridges(
    color = "white",
    quantile_lines = TRUE,
    scale = 1.3,
    alpha = 0.8,
    show.legend = FALSE
  ) +
  scale_x_continuous(n.breaks = 8) +
  ggplot2::xlab("Weekly Score") +
  ggplot2::ylab(NULL) +
  ggplot2::theme_minimal() +
  ggplot2::theme(
    panel.grid.major.y = ggplot2::element_blank(),
    plot.title.position = "plot"
  ) +
  ggplot2::labs(
    title = glue::glue("Week Scores - {sims} Simulated Weeks"),
    subtitle = glue::glue("{league_info$league_name}")
  )

```

Using the outputs from above, the next chart shows the probability of each team of winning the week `r gameweek_end+1` matchup against their opponent.

``` {r upcoming week win probability, echo = F, message = F, warning = F, dev.args = list(bg = 'transparent')}

summary_week_weekly %>% 
  filter(week==gameweek_end+1) %>% 
  left_join(matchup_id[, c('roster_id', 'gameweek', 'matchup_id')], by = c('franchise_id'='roster_id', 'week'='gameweek')) %>% 
  group_by(Manager, matchup_id) %>% 
  summarise(Wins = sum(selected_win)/sims) %>% 
  group_by(matchup_id) %>% 
  arrange(matchup_id, desc(Manager)) %>% 
  mutate(matchup_name = if_else(row_number()%%2==0, paste(Manager, lag(Manager), sep = ' vs '), paste(lead(Manager), Manager, sep = ' vs ')),
         ypos = cumsum(Wins)-0.5*Wins) %>% 
  ggplot(aes(x=factor(1), y = Wins, fill = Manager)) +
  ggplot2::geom_bar(width=1, stat = 'identity') +
  coord_polar('y') +
  ggplot2::facet_wrap(~matchup_name) +
  geom_text(aes(y = ypos, label = percent(Wins, accuracy = 0.1)), color = "white", size=4) +
  theme_void() +
  ggplot2::theme(
    plot.title = element_text(margin=margin(0,0,10,0)),
  ) +
  ggplot2::labs(
    title = glue::glue("Week {gameweek_end+1} Win Probability - {sims} Simulated Weeks")
  )

```

------------------------------------------------------------------------

# Story of the Season

The following chart shows the performance of each team as the season has progressed. This is calculated as the xWins for each week minus the average wins each week (0.5). This strips out any influence of matchup and purely looks at your points position in a given week.

For example, an increasing line in the first half of the season followed by a decreasing line over the second half would signify good performance to start the year, but a poor run to end the season.

```{r xwins vs average, echo = F, message = F}

xWins_vs_avg <- pts_week %>% 
  filter(gameweek<=gameweek_end) %>% 
  mutate(xWins = all_play/11) %>% 
  group_by(Manager) %>% 
  mutate(cum_Wins = cumsum(win),
         cum_xWins = round(cumsum(xWins), 1),
         win_diff = cum_xWins - gameweek/2)

div(xWins_vs_avg %>% 
  ungroup() %>% 
  plot_ly(y = ~win_diff) %>% 
  add_trace(x = ~gameweek, color = ~Manager, type = 'scatter', mode = ifelse(gameweek_end==1, '', 'lines'), colors = 'Paired', text = ~Manager,
            hovertemplate = paste('Week %{x}', '<br>%{text}', '<br>xWins vs Avg: %{y}', '<extra></extra>')) %>% 
  layout(title = 'xWins vs Average over the Season',
         xaxis = list(title = 'Week',fixedrange = TRUE, tickmode = 'linear'),
         yaxis = list(title = 'xWins vs Average',  categoryorder = "array", categoryarray = ~win_diff, tick0=1, dtick=1, fixedrange = TRUE),
         legend = list(title=list(text='<b> Manager </b>')),
         paper_bgcolor = 'transparent', plot_bgcolor = 'transparent'), align = 'left')


```

------------------------------------------------------------------------

# League Position Tracker

The next table tracks the league position by week for each team in the league. To isolate a single team's record, double click on the legend on the right.

```{r position chart, echo = F, message = F}

position <- pts_week %>% 
  filter(gameweek<=gameweek_end) %>% 
  group_by(Manager) %>% 
  summarise(csum_win = cumsum(win),
            csum_pts = cumsum(pts)) %>% 
  mutate(gameweek = rep(1:gameweek_end)) %>% 
  ungroup() %>% 
  group_by(gameweek) %>% 
  mutate(Position = league_size + 1 - rank(csum_win + csum_pts/10000))

div(position %>% 
  ungroup() %>% 
  plot_ly(y = ~Position) %>% 
  add_trace(x = ~gameweek, color = ~Manager, type = 'scatter', mode = 'lines+markers', colors = 'Paired', text = ~Manager, color = ~Manager,
            hovertemplate = paste('Week %{x}', '<br>%{text}', '<br>Position: %{y}', '<extra></extra>')) %>% 
  layout(title = 'League Position by Week',
         xaxis = list(title = 'Week',fixedrange = TRUE, tickmode = 'linear'),
         yaxis = list(title = 'League Position',  categoryorder = "array", categoryarray = ~Position, autorange = 'reversed', tick0=1, dtick=1,
                      range=c(1,12), fixedrange = TRUE),
         legend = list(orientation = 'h', y = -0.3),
         paper_bgcolor = 'transparent', plot_bgcolor = 'transparent'), align = 'left')

```

------------------------------------------------------------------------

# Matchup Importance

The following table shows the importance of the next matchup for each manager. Win shows the Playoff % if the matchup is won, and Loss shows the chances with a loss. The Current % is the playoff probability before week `r gameweek_end + 1` takes place. The size of the bar represents the importance of the matchup for each team.

``` {r playoff leverage, echo = F, message = F}

playoff_leverage <- table_sim %>% 
  group_by(Manager, Upcoming) %>% 
  summarise(Playoff = round(mean(Playoff), 3)*100) %>% 
  pivot_wider(names_from = 'Upcoming', values_from = 'Playoff') %>% 
  rename(Win = `1`, Loss = `0`) %>% 
  mutate(Difference = Win - Loss) %>% 
  arrange(desc(Difference)) %>% 
  left_join(pts_season[, c('Manager', 'Playoff %')], by = 'Manager') %>%
  rename(Current = `Playoff %`) %>% 
  ungroup()

div(playoff_leverage %>%
  arrange(desc(Current)) %>% 
  plot_ly(x = ~Manager) %>% 
  add_trace(y = ~Loss, type = 'bar', hoverinfo = 'skip', marker = list(color = 'rgba(1,1,1, 0.0)')) %>% 
  add_trace(y = ~Difference, marker = list(color = 'rgba(55, 128, 191, 0.7)',
                                           line = list(color = 'rgba(55, 128, 191, 0.7)',
                                                       width = 2)),
            text = ~paste0('<b>', Manager, '</b><br>Win: ', Difference + Loss, '% <br>Current: ', Current, '% <br>Loss: ', Loss, '%'),
            hovertemplate = paste('%{text}', '<extra></extra>'), textposition = 'none') %>% 
  add_trace(y = ~Current, type = 'scatter', mode = 'markers', hoverinfo = 'skip', marker = list(size = 5,
                                                                                                color = 'rgba(255, 182, 193, .9)')) %>% 
  layout(title = 'Playoff Probability by Next Result',
         xaxis = list(title = "",
                      categoryorder = "array",
                      categoryarray = c(~Current),
                      fixedrange = TRUE),
         yaxis = list(title = "",
                      fixedrange = TRUE),
         barmode = 'stack',
         showlegend = FALSE,
         hovermode = 'x',
         paper_bgcolor = 'transparent', plot_bgcolor = 'transparent'), align = 'left')

```

<br>

Using this information, we can calculate the importance of each matchup in week `r gameweek_end + 1`. The numbers shown give the average playoff leverage for each matchup.

``` {r playoff leverage matchup, echo = F, message = F}

matchup_imp <- matchup_id %>% 
  filter(gameweek==gameweek_end+1) %>% 
  left_join(user_info[, c('roster_id', 'Manager')], by = 'roster_id') %>% 
  left_join(user_info[, c('roster_id', 'Manager')], by = c('opponent_id' = 'roster_id')) %>% 
  mutate(roster_id  = as.numeric(roster_id)) %>% 
  arrange(matchup_id, roster_id) %>% 
  ungroup() %>% 
  filter(matchup_id==lead(matchup_id)) %>% 
  left_join(playoff_leverage[, c('Manager', 'Difference')], by =c('Manager.x' = 'Manager')) %>% 
  left_join(playoff_leverage[, c('Manager', 'Difference')], by =c('Manager.y' = 'Manager')) %>% 
  mutate(Mean_diff = round((Difference.x + Difference.y)/2, 1)) %>% 
  arrange(desc(Mean_diff)) %>% 
  select(Manager.x, Mean_diff, Manager.y)

matchup_imp %>% 
  knitr::kable(format = 'html', align = c('r', 'c', 'l'), escape = F, col.names = NULL) %>% 
  kable_styling(bootstrap_options = c('striped', 'responsive', 'hover'),
                full_width = F,
                position = 'left') %>% 
  column_spec(2, background = spec_color(matchup_imp$Mean_diff, begin = 0.2, end = 0.8, option = 'A', alpha = 0.3, direction = -1))

```

------------------------------------------------------------------------

# Potential Points

The following table shows the potential points that could have been scored if the perfect squad had been played each week.

```{r pp table, echo = F}

pp_season %>% 
  arrange(Points) %>% 
  mutate(Rank = 13-row_number()) %>%
  arrange(Rank) %>% 
  select(-Wins) %>% 
  knitr::kable(format = 'html', align = c('c', 'l', 'c')) %>% 
  kable_styling(bootstrap_options = c('striped', 'responsive'),
                full_width = F,
                position = 'left')

```

The matchups for week `r gameweek_end` are shown below, along with the potential points for each matchup.

```{r pp matchup, echo = F}

myHeader_init <- paste('Week ', gameweek_end, ' Potential Points Matchups', sep = '')
myHeader <- c(myHeader_init = 4)
names(myHeader) <- c(myHeader_init)

pp_weekly_matchup$Manager.x <- ifelse(pp_weekly_matchup$pp.x>pp_weekly_matchup$pp.y, cell_spec(pp_weekly_matchup$Manager.x, color = 'white', background = '#79c973', bold = T), cell_spec(pp_weekly_matchup$Manager.x, color = 'white', background = '#ff6666'))
pp_weekly_matchup$Manager.y <- ifelse(pp_weekly_matchup$pp.x<pp_weekly_matchup$pp.y, cell_spec(pp_weekly_matchup$Manager.y, color = 'white', background = '#79c973', bold = T), cell_spec(pp_weekly_matchup$Manager.y, color = 'white', background = '#ff6666'))

pp_weekly_matchup %>% 
  select(Manager.x, pp.x, pp.y, Manager.y) %>%
  knitr::kable(format = 'html', align = c('r', 'c', 'c', 'l'), col.names = NULL, escape = F) %>% 
  kable_styling(bootstrap_options = c('striped', 'responsive'),
                full_width = F,
                position = 'left') %>% 
  add_header_above(header = myHeader)
rm(myHeader, myHeader_init)

```

```{r projected draft picks, echo = F}

picksRaw <- GET(paste("https://api.sleeper.app/v1/league/",league_id,"/traded_picks",sep=""))
picksParsed <- content(picksRaw, as="parsed")

datalist_picks = list()
for (i in 1:length(picksParsed)) {
  
  df <- data.frame(t(unlist(picksParsed[[i]])))
  
  datalist_picks[[i]] <- df
}
traded_picks <- bind_rows(datalist_picks) %>% 
  mutate(pick_name = paste0(season, ' Mid ', round, if_else(round=='1', 'st',
                                                            if_else(round=='2', 'nd',
                                                                    if_else(round=='3', 'rd', 'th')))))
rm(picksParsed, picksRaw, i, datalist_picks)

projected_draft <- pp_season %>% 
  left_join(pts_season[, c('Manager', 'Position', 'Wins')], by = 'Manager', suffix = c('', '_Actual')) %>% 
  rename(Actual_Position = Position) %>% 
  mutate(Temp_Rank = rank(if_else(Actual_Position<=6, Actual_Position, as.double(Rank)+100)),
         Rank = league_size + 1 - Temp_Rank) %>% 
  select(Rank, Manager) %>% 
  arrange(Rank) %>% 
  slice(rep(1:n(), each = 4)) %>% 
  mutate(Round = rep(c('1', '2', '3', '4'), league_size)) %>% 
  arrange(Round, Rank) %>% 
  left_join(user_info[, c('Manager', 'roster_id')], by = 'Manager') %>% 
  left_join(traded_picks[traded_picks$season==season+1,], by = c('roster_id', 'Round' = 'round')) %>% 
  left_join(user_info[, c('roster_id', 'Manager')], by = c('owner_id' = 'roster_id')) %>% 
  rename(Original_Owner = Manager.x, Owner = Manager.y, Pick = Rank) %>% 
  mutate(Owner = if_else(is.na(Owner), Original_Owner, Owner),
         `Original Owner` = if_else(Original_Owner==Owner, '', Original_Owner)) %>% 
  select(Round, Pick, Owner, `Original Owner`)

```

------------------------------------------------------------------------

# Draft Picks

## Projected Draft Order{.tabset .tabset-fade}

The `r draft_rounds` rounds of the `r (season+1)` rookie draft are shown below, using the potential points order as at today.

### Round 1

```{r round1, echo=F}

projected_draft_table <- projected_draft %>%
  filter(Round==1)

projected_draft_table %>% 
  select(-Round) %>% 
  knitr::kable(format = 'html', align = c('c', 'l', 'c')) %>%
  kable_styling(bootstrap_options = c('striped', 'responsive'),
                full_width = F,
                position = 'left') %>% 
  row_spec(which(projected_draft_table$`Original Owner`!=''), bold = T, color = "white", background = "#feb9b9")

```

### Round 2

```{r round2, echo=F}

projected_draft_table <- projected_draft %>%
  filter(Round==2)

projected_draft_table %>% 
  select(-Round) %>% 
  knitr::kable(format = 'html', align = c('c', 'l', 'c')) %>%
  kable_styling(bootstrap_options = c('striped', 'responsive'),
                full_width = F,
                position = 'left') %>% 
  row_spec(which(projected_draft_table$`Original Owner`!=''), bold = T, color = "white", background = "#feb9b9")

```

### Round 3

```{r round3, echo=F}

projected_draft_table <- projected_draft %>%
  filter(Round==3)

projected_draft_table %>% 
  select(-Round) %>% 
  knitr::kable(format = 'html', align = c('c', 'l', 'c')) %>%
  kable_styling(bootstrap_options = c('striped', 'responsive'),
                full_width = F,
                position = 'left') %>% 
  row_spec(which(projected_draft_table$`Original Owner`!=''), bold = T, color = "white", background = "#feb9b9")

```

### Round 4

```{r round4, echo=F}

projected_draft_table <- projected_draft %>%
  filter(Round==4)

projected_draft_table %>% 
  select(-Round) %>% 
  knitr::kable(format = 'html', align = c('c', 'l', 'c')) %>%
  kable_styling(bootstrap_options = c('striped', 'responsive'),
                full_width = F,
                position = 'left') %>% 
  row_spec(which(projected_draft_table$`Original Owner`!=''), bold = T, color = "white", background = "#feb9b9")
rm(projected_draft_table)

```

<br>

## Draft Pick Likelihood

The following chart shows the likelihood of drafting at each position in the top 6. Picks 7-12 have been removed as the playoffs determine the back half of the first round.

``` {r draft position probability, echo=F, message=F, warning=F}

max_prob = max(sim_draft[2:7])
min_prob = min(sim_draft[2:7])
mid_prob = max_prob-min_prob

pal <- scales::gradient_n_pal(colours = c('#f87274', '#FCB9BA', '#ffffff'),values= c(max_prob, mid_prob, min_prob))
# pal <- scales::gradient_n_pal(colours = c('#f87274', '#63be7b'),values= c(min_prob, max_prob))

draft_color <- sim_draft %>% 
  pivot_longer(cols = 2:7, names_to = 'Pick', values_to = 'Probability') %>% 
  mutate(color_values = pal(Probability)) %>% 
  select(-Probability) %>% 
  pivot_wider('Manager', names_from = 'Pick', values_from = 'color_values') %>% 
  replace(is.na(.), '#FFFFFF')

percent_0.1 <- function(x) (percent(x, 0.1))

sim_draft %>% 
  mutate_at(2:8, percent_0.1) %>% 
  kable(format = 'html', escape = F, align = c('l', rep('c', 7)),
        col.names = c('', '1', '2', '3', '4', '5', '6', 'Playoffs')) %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'responsive'), full_width = F,
                position = 'l') %>% 
  column_spec(1, color = 'black') %>% 
  column_spec(2, color = 'black', background = draft_color[[2]]) %>% 
  column_spec(3, color = 'black', background = draft_color[[3]]) %>% 
  column_spec(4, color = 'black', background = draft_color[[4]]) %>% 
  column_spec(5, color = 'black', background = draft_color[[5]]) %>% 
  column_spec(6, color = 'black', background = draft_color[[6]]) %>% 
  column_spec(7, color = 'black', background = draft_color[[7]]) %>% 
  add_header_above(c(" " = 1, "Draft Pick" = 6, " " = 1))

```


------------------------------------------------------------------------

# Roster Comparison

## Dynasty

The value of each roster has been calculated using crowdsourced values from [KeepTradeCut](https://keeptradecut.com/dynasty-rankings). A value is calculated for each player and these are totaled.

Draft picks for the next 2 years are also included in the estimate, but given how difficult it is to value future picks, these have been assumed to fall in the middle of the given round.

```{r roster comparison dynasty, echo = F, message = F}

rosters <- rosters %>% 
  left_join(traded_picks[, c('owner_id', 'roster_id', 'pick_name')], by = c('roster_id', 'full_name' = 'pick_name'), suffix = c('', '.new')) %>% 
  mutate(owner_id.new = if_else(is.na(owner_id.new), roster_id, owner_id.new),
         position = if_else(str_detect(player_no, 'pick'), 'Draft', position)) %>% 
  left_join(df_KTC_join[, c('player_id', 'Value')], by = 'player_id') %>%
  left_join(df_KTC_join[, c('Player', 'Value')], by = c('player_id' = 'Player'), suffix = c('', '.draft')) %>% 
  mutate(Value = if_else(is.na(Value), Value.draft, Value)) %>% 
  left_join(user_info[, c('roster_id', 'Manager')], by = c('owner_id.new' = 'roster_id'), suffix = c('', '.new')) %>% 
  mutate(Manager = Manager.new) %>% 
  select(-Value.draft, -Manager.new)
  
dynasty_roster_value <- rosters %>% 
  filter(!is.na(Value)) %>%
  group_by(Manager) %>%
  summarise(Value = sum(Value, na.rm = T)) %>% 
  arrange(desc(Value)) %>% 
  ungroup() %>% 
  mutate(Value_Std = round(Value/max(Value)*100, 1))
  
dynasty_roster_value_pos <- rosters %>% 
  filter(!is.na(Value)) %>% 
  mutate(position = factor(position, levels = c('TE', 'WR', 'RB', 'QB', 'Draft'))) %>% 
  group_by(Manager, position) %>%
  summarise(Value = round(sum(Value, na.rm = T)/max(dynasty_roster_value$Value)*100, 1)) %>% 
  arrange(desc(Value)) %>% 
  ungroup()

div(dynasty_roster_value_pos %>% 
  plot_ly(y = ~Value) %>% 
  add_trace(x = ~Manager, type = 'bar', color = ~position) %>% 
  layout(barmode = 'stack',
         title = 'Dynasty Value of Each Team by Position Group',
         hovermode = 'compare',
         xaxis = list(title = 'Team', categoryorder = "array", categoryarray = ~dynasty_roster_value$Manager, fixedrange = TRUE),
         yaxis = list(title = 'Dynasty Value', fixedrange = TRUE),
         paper_bgcolor = 'transparent', plot_bgcolor = 'transparent'), align = 'left')


```

## Contender

The following chart uses a similar concept, but looks at the value of the squad for this season. The chart above will take into account the long term value of a player, whereas this chart purely looks at squad value for the remainder of this season. Any injuries will affect the value and immediate competitiveness of each team.

```{r roster comparison fantasy, echo = F, message = F}

rosters <- rosters %>% 
  left_join(df_KTC_fantasy_join[, c('player_id', 'Value')], by = 'player_id', suffix = c('', '.contender')) 
  
fantasy_roster_value <- rosters %>% 
  filter(!is.na(Value.contender)) %>%
  group_by(Manager) %>%
  summarise(Value = sum(Value.contender, na.rm = T)) %>% 
  arrange(desc(Value)) %>% 
  ungroup() %>% 
  mutate(Value_Std = round(Value/max(Value)*100, 1))
  
fantasy_roster_value_pos <- rosters %>% 
  filter(!is.na(Value.contender)) %>% 
  mutate(position = factor(position, levels = c('TE', 'WR', 'RB', 'QB'))) %>% 
  group_by(Manager, position) %>%
  summarise(Value = round(sum(Value.contender, na.rm = T)/max(fantasy_roster_value$Value)*100, 1)) %>% 
  arrange(desc(Value)) %>% 
  ungroup()

div(fantasy_roster_value_pos %>% 
  plot_ly(y = ~Value) %>% 
  add_trace(x = ~Manager, type = 'bar', color = ~position) %>% 
  layout(barmode = 'stack',
         title = 'Immediate Value of Each Team by Position Group',
         hovermode = 'compare',
         xaxis = list(title = 'Team', categoryorder = "array", categoryarray = ~fantasy_roster_value$Manager, fixedrange = TRUE),
         yaxis = list(title = 'Immediate Value', fixedrange = TRUE),
         paper_bgcolor = 'transparent', plot_bgcolor = 'transparent'), align = 'left')


```

## Roster Maturity

This chart shows the spread of ages on each roster within the league. The narrower the box, the more concentrated the ages are, and the larger boxes will have a wide spread of ages.

```{r roster age comparison, echo = F, message = F, warning = F}

roster_age <- rosters %>% tibble() %>% 
  left_join(player_data[, c('birth_date', 'player_id')], by = 'player_id') %>%
  mutate(birth_date = as.Date(birth_date),
         age = interval(birth_date, Sys.Date()) / years(1))

mean_roster_age <- roster_age %>% group_by(Manager) %>% summarise(mean = mean(age, na.rm = T)) %>% arrange(desc(mean))

div(roster_age %>% 
  plot_ly(y=~age, color=~Manager, type='box', boxmean = T, hoverinfo='none') %>% 
  layout(title = 'Boxplot of Player Age by Team',
         xaxis = list(title = 'Team', categoryorder = "array", categoryarray = ~mean_roster_age$Manager, fixedrange = TRUE),
         yaxis = list(title = 'Player Age', fixedrange = TRUE),
         paper_bgcolor = 'transparent', plot_bgcolor = 'transparent'), align = 'left')

```

------------------------------------------------------------------------

# 2022 Trades

```{r trades, echo=F}

transactions <- ff_transactions(dynasty_conn) %>% 
  left_join(user_info[, c('roster_id', 'Manager')], by = c('franchise_id' = 'roster_id'))

#wrapping div round (and aligning left) helps to format the graph

div(transactions %>% 
  filter(type == 'trade') %>% 
  select(timestamp, type, Manager) %>% 
  distinct() %>%
  group_by(Manager) %>% 
  summarise(Trade_Count = n()) %>%
  arrange(desc(Trade_Count)) %>% 
  plot_ly(y = ~Trade_Count) %>% 
  add_trace(x = ~Manager, type = 'bar') %>% 
  layout(title = ' Number of 2022 Trades by Team',
         xaxis = list(title = 'Team', categoryorder = "array", categoryarray = ~Trade_Count, fixedrange = TRUE),
         yaxis = list(title = 'Number of Trades', fixedrange = TRUE),
         paper_bgcolor = 'transparent', plot_bgcolor = 'transparent'), align = 'left')


```
